--- 
title: "Making Lecture Notes with Bookdown"
author: "Vicky Scowcroft"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    #css: "mystyle.css"
    split_by: rmd
documentclass: book
bibliography: [book.bib, packages.bib]
csl: apj.csl
subparagraph: yes
link-citations: yes
github-repo: vickyscowcroft/bookdown_lecture_notes_guide
description: "Guide for creating html lecture notes using Bookdown"
---
\newcommand{\AA}{\unicode{x0212B}}
# Introduction {-}

This guide walks through how to create html lecture notes using **R**, **Markdown** and **Bookdown**. This format is preferred as LaTeX doesn't play nicely with accessibility tools like screen readers, especially for maths heavy content. 

## System Requirements {-}

To use bookdown, you will need to have R and R studio installed (perhaps R studio is not a requirement, but it makes things a lot easier). These can both be installed from the DDAT Self Service app on a Mac, or R can be downloaded directly from [here](https://cran.r-project.org/) and R Studio from [here](https://rstudio.com/products/rstudio/download/). You will also need [**pandoc**](https://pandoc.org/index.html). This may already be installed on your system as part of the Anaconda distribution.

The [**bookdown**](https://bookdown.org/yihui/bookdown/) package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


## Caveat {-}

The instructions in this guide are what worked for me, on a Mac using R version 4.2.1, R Studio version 2022.07.1 and pandoc version 2.18 (updated August 2022). This guide also assumes that you're familiar with using the command line.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
## setup wordwrap
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```


